---
title: "Covid-19"
output: 
  flexdashboard::flex_dashboard:
    css: style.css
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(magrittr)
library(xts)
library(plotly)
library(dplyr)

# hex msafra: #4c1211
# rgb msafra: 761817

gcal <- c("#039be5", "#7986cb", "#33b679", "#8e24aa", "#e67c73", "#f6c026", "#f5511d",	"#039be5", "#616161", "#3f51b5", "#0b8043", "#d60000")
ncal <- c('#5484ed','#a4bdfc','#46d6db', '#7ae7bf', '#51b749', '#fbd75b', '#ffb878', '#ff887c', '#dc2127', '#dbadff', '#e1e1e1')
hcal <- c('#f2aa0e', '#aa1717', '#3d8e53', '#3d8e72')

lcolors <- c("#000000"   # China
            ,"#d0cece"   # Japan
            ,"#7f7f7f"   # Singapore
            ,"#4c1211"   # Korea, South
            ,"#007c00"   # Germany
            ,"#ffc000"   # Italy
            ,"#00b050"   # France
            ,"#f8dddc"   # Spain
            ,"#bfe4ff"   # Mexico
            ,"#ffff00"   # Brazil
            ,"#bbffda")  # US

names(lcolors) <- c("China"
                   ,"Japan"
                   ,"Singapore"
                   ,"Korea, South"
                   ,"Germany"
                   ,"Italy"
                   ,"France"
                   ,"Spain"
                   ,"Mexico"
                   ,"Brazil"
                   ,"US")

#========================================
# This is bold blue: '#5484ed'
# This is blue: '#a4bdfc'
# This is turquoise: '#46d6db'
# This is green: '#7ae7bf'
# This is bold green: '#51b749'
# This is yellow:'#fbd75b'
# This is orange: '#ffb878'
# This is red: '#ff887c'
# This is bold red: '#dc2127'
# This is purple: '#dbadff'
# This is gray: '#e1e1e1'
#=======================================
# This is unknown: '#039be5'
# This is Lavender: '#7986cb' 
# This is Sage: '#33b679'     
# This is Grape: '#8e24aa'
# This is Flamingo:	'#e67c73'
# This is Banana:	'#f6c026'
# This is Tangerine: '#f5511d'
# This is Peacock: '#039be5'
# This is Graphite:	'#616161'
# This is Bluberry:	'#3f51b5'
# This is Basil: '#0b8043'
# This is Tomato:	'#d60000'
#=======================================
# This is orange: '#f2aa0e'
# This is dark red: '#aa1717'
# This is green: '#3d8e53'
# This is water green: '#3d8e72'

plot.fl <- function(ts, title = '', colorset = c(gcal[1], ncal[7])) {
    require(PerformanceAnalytics)
    chart.TimeSeries(ts, main = title, colorset = colorset, legend.loc = 'topleft')
}

chart.fl <- function(ts, title = '', colorset = c(gcal[1],ncal[7])) {
    require(dygraphs)
    dygraph(ts, main = title, group = 'master') %>% 
    dyOptions(colors = colorset, axisLineWidth = .5, gridLineColor = 'lightgray') %>%
    #dyRangeSelector(height = 10, strokeColor = '') %>%
    dyHighlight(highlightSeriesBackgroundAlpha = 0.8) %>%
    dyLegend(show = 'auto', width = 560, hideOnMouseOut = TRUE)
}
```

Todos os Países
======================================================================

Column {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Evolução de Casos Países
```{r}
download <- RCurl::getURL("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")

# Watch out the time of updating
dias <- round(difftime(Sys.Date(), "2020-01-22", units = "days"), 0) + 4

data_wc <- read.csv(text = download, 
                   stringsAsFactors = FALSE, 
                   colClasses = c(rep('character', 4), rep('numeric', dias - 4)))

dates <- colnames(data_wc)[-c(1:4)] %>% 
         strsplit(., 'X') %>% 
         lapply(., '[', 2) %>% 
         unlist() %>% 
         as.Date(format = "%m.%d.%y")
colnames(data_wc) <- c(colnames(data_wc)[1:4], format(dates, '%m/%d/%y'))

Countries_wc <- unique(data_wc[,2])
Cases <- list()
for (i in 1:length(Countries_wc)) {
    Cases[[i]] <- filter(data_wc, Country.Region == Countries_wc[i])[,-c(1:4)]  %>% colSums()  %>% as.vector()
}
names(Cases) <- Countries_wc

NewData_wc <- t(do.call(cbind, Cases))
colnames(NewData_wc) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wc)
DT::datatable(NewData_wc[,(N-4):N], 
              options = list(order = list(list(5, 'desc'))
)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```

Column {data-width=350}
-----------------------------------------------------------------------

### Total de Mortos
```{r}
download <- RCurl::getURL("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")

data_wd <- read.csv(text = download, 
                 stringsAsFactors = FALSE, 
                 colClasses = c(rep('character', 4), rep('numeric', dias-4)))

Countries_wd <- unique(data_wd[,2])
Death <- list()
for (i in 1:length(Countries_wd)) {
    Death[[i]] <- filter(data_wd, Country.Region == Countries_wd[i])[,-c(1:4)]  %>% colSums()  %>% as.vector()
}
names(Death) <- Countries_wd

NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wd)
DT::datatable(NewData_wd[,(N-4):N], 
              options = list(order = list(list(5, 'desc'))
)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')

```

Cases {data-navmenu='Europa'} 
==========================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Total Cases
```{r}
SelectedCountries <- c("Italy"
                      ,"Spain"
                      ,"Germany"
                      ,"France"
                      ,"United Kingdom"
                      ,"Switzerland"
                      ,"Belgium"
                      ,"Netherlands"
                      ,"Austria"
                      ,"Portugal"
                      ,"Sweden"
                      ,"Norway"
                      ,"Denmark"
                      ,"Ireland"
                      ,"Romania"
                      ,"Luxembourg"
                      ,"Finland"
                      ,"Greece"
                      ,"Poland"
                      ,"Kosovo")


N = ncol(NewData_wc)
DT::datatable(NewData_wc[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
  
```


Column {data-width=350}
-----------------------------------------------------------------------

### New Cases
```{r}

dife_c<-NewData_wc[, -1, drop = FALSE] - NewData_wc[, -ncol(NewData_wc), drop = FALSE]

N = ncol(dife_c)
DT::datatable(dife_c[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```


Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}

porce_c<-round(((NewData_wc[, -1, drop = FALSE] - NewData_wc[, -ncol(NewData_wc), drop = FALSE])/NewData_wc[, -ncol(NewData_wc), drop = FALSE]*100),2)

N = ncol(porce_c)
DT::datatable(porce_c[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```



Deaths {data-navmenu='Europa'} 
==========================================================================


Column {data-width=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wd)
DT::datatable(NewData_wd[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt') 
  

```

Column {data-width=350}
-----------------------------------------------------------------------

### New Deaths
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")



dife_d<-NewData_wd[, -1, drop = FALSE] - NewData_wd[, -ncol(NewData_wd), drop = FALSE]

N = ncol(dife_d)
DT::datatable(dife_d[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')


```

Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

porce_d<-round(((NewData_wd[, -1, drop = FALSE] - NewData_wd[, -ncol(NewData_wd), drop = FALSE])/NewData_wd[, -ncol(NewData_wd), drop = FALSE]*100),2)

N = ncol(porce_d)
DT::datatable(porce_d[SelectedCountries,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')

```





Cases {data-navmenu='US'} 
==========================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Total Cases
```{r}
 names_us <- t(data.frame("US","New York", "New Jersey", "Michigan", "California", "Massachusetts", "Florida", "Illinois", "Louisiana", "Washington", "Pennsylvania", "Georgia", "Texas", "Connecticut", "Colorado", "Tennessee", "Ohio", "Indiana", "Maryland", "Others"))


download_us <- RCurl::getURL("https://raw.githubusercontent.com/COVID19Tracking/covid-tracking-data/master/data/states_daily_4pm_et.csv")

data_us <- read.csv(text = download_us)

data_us[is.na(data_us)] <- 0

data_us_cases <- data_us %>% 
                    select("positive","state","dateChecked") %>%
                    arrange(dateChecked) %>%
                    ungroup()

data_us_cases<-reshape(data_us_cases, v.names = "positive", idvar="state", direction = "wide", timevar = "dateChecked")





date_us_cases <- vapply(strsplit(colnames(data_us_cases)[-1], "positive."), '[', character(1), 2) %>% as.Date



colnames(data_us_cases) <- c("state" ,format(date_us_cases,"%m/%d/%y"))
rownames(data_us_cases) <- data_us_cases[,1]
data_us_cases <- data_us_cases[,-1]




total_us <- (data.frame(colSums(data_us_cases)))



soma_us_v <- (data.frame(colSums(data_us_cases[c("NY"
                        ,"NJ"
                        ,"MI"
                        , "CA"
                        , "MA"
                        , "FL"
                        , "IL"
                        , "LA"
                        , "WA"
                        , "PA"
                        , "GA"
                        , "TX"
                        , "CT"
                        , "CO"
                        , "TN"
                        , "OH"
                        , "IN"
                        , "MD"),])))



other_us <- t(total_us - soma_us_v)
total_us <- t(total_us)

soma_us_b <- rbind(total_us, other_us)






rownames(soma_us_b)[1]<-"US"
rownames(soma_us_b)[2]<-"Others"

data_us_cases <- rbind(data_us_cases, soma_us_b)



 Selectedstate_us <- c("US"
                        ,"NY"
                        ,"NJ"
                        ,"MI"
                        , "CA"
                        , "MA"
                        , "FL"
                        , "IL"
                        , "LA"
                        , "WA"
                        , "PA"
                        , "GA"
                        , "TX"
                        , "CT"
                        , "CO"
                        , "TN"
                        , "OH"
                        , "IN"
                        , "MD"
                        , "Others"
                          )

N = ncol(data_us_cases)
data_us_cases_t <- data_us_cases[Selectedstate_us,(N-4):N]
rownames(data_us_cases_t) <- c(names_us)

 
 

DT::datatable(data_us_cases_t, options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')



 

 
 


  
```


Column {data-width=350}
-----------------------------------------------------------------------

### New Cases
```{r}

dife_c_us<-data_us_cases[, -1, drop = FALSE] - data_us_cases[, -ncol(data_us_cases), drop = FALSE]



N = ncol(dife_c_us)
dife_c_us_t <- dife_c_us[Selectedstate_us,(N-4):N]
rownames(dife_c_us_t) <- c(names_us)

DT::datatable(dife_c_us_t,options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```


Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}

porce_c_us<-round(((data_us_cases[, -1, drop = FALSE] - data_us_cases[, -ncol(data_us_cases), drop = FALSE])/data_us_cases[, -ncol(data_us_cases), drop = FALSE]*100),2)

N = ncol(porce_c_us)
porce_c_us_t <- porce_c_us[Selectedstate_us,(N-4):N]
rownames(porce_c_us_t) <- c(names_us)

DT::datatable(porce_c_us_t,options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```



Deaths {data-navmenu='US'} 
==========================================================================


Column {data-width=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}

data_us_deaths <- data_us %>% 
                    select("death","state","dateChecked") %>%
                    arrange(dateChecked) %>%
                    ungroup()

data_us_deaths<-reshape(data_us_deaths, v.names = "death", idvar="state", direction = "wide", timevar = "dateChecked")





date_us_deaths <- vapply(strsplit(colnames(data_us_deaths)[-1], "death."), '[', character(1), 2) %>% as.Date



colnames(data_us_deaths) <- c("state" ,format(date_us_deaths,"%m/%d/%y"))
rownames(data_us_deaths) <- data_us_deaths[,1]
data_us_deaths <- data_us_deaths[,-1]




total_us_d <- (data.frame(colSums(data_us_deaths)))



soma_us_v <- (data.frame(colSums(data_us_deaths[c("NY"
                        ,"NJ"
                        ,"MI"
                        , "CA"
                        , "MA"
                        , "FL"
                        , "IL"
                        , "LA"
                        , "WA"
                        , "PA"
                        , "GA"
                        , "TX"
                        , "CT"
                        , "CO"
                        , "TN"
                        , "OH"
                        , "IN"
                        , "MD"),])))



other_us <- t(total_us_d - soma_us_v)
total_us_d <- t(total_us_d)

soma_us_b <- rbind(total_us_d, other_us)






rownames(soma_us_b)[1]<-"US"
rownames(soma_us_b)[2]<-"Others"

data_us_deaths <- rbind(data_us_deaths, soma_us_b)



N = ncol(data_us_deaths)
data_us_deaths_t <- data_us_deaths[Selectedstate_us,(N-4):N]
rownames(data_us_deaths_t) <- c(names_us)

DT::datatable(data_us_deaths_t,options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
  

```

Column {data-width=350}
-----------------------------------------------------------------------

### New Deaths
```{r}


dife_d_us<-data_us_deaths[, -1, drop = FALSE] - data_us_deaths[, -ncol(data_us_deaths), drop = FALSE]

N = ncol(dife_d_us)
dife_d_us_t <- dife_d_us[Selectedstate_us,(N-4):N]
rownames(dife_d_us_t) <- c(names_us)

DT::datatable(dife_d_us_t,options = list(
  pageLength = 20,paging = FALSE,searching = FALSE))%>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')


```

Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}


porce_d_us<-round(((data_us_deaths[, -1, drop = FALSE] - data_us_deaths[, -ncol(data_us_deaths), drop = FALSE])/data_us_deaths[, -ncol(data_us_deaths), drop = FALSE]*100),2)

N = ncol(porce_d_us)
porce_d_us_t <- porce_d_us[Selectedstate_us,(N-4):N]
rownames(porce_d_us_t) <- c(names_us)

DT::datatable(porce_d_us_t,options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')

```









################################################





Cases {data-navmenu='Brasil'} 
==========================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Total Cases
```{r}

download_br <- RCurl::getURL("https://raw.githubusercontent.com/wcota/covid19br/master/cases-brazil-states.csv")

data_br <- read.csv(text = download_br)

data_br_cases<-reshape(data_br, v.names = "totalCases", idvar="state", direction = "wide", timevar = "date", drop=c("city","country","deaths","newCases"))




date_br_cases <- vapply(strsplit(colnames(data_br_cases)[-1], "totalCases."), '[', character(1), 2) %>% as.Date

colnames(data_br_cases) <- c("state" ,format(date_br_cases,"%m/%d/%y"))
rownames(data_br_cases) <- data_br_cases[,1]
data_br_cases <- data_br_cases[,-1]
rownames(data_br_cases)[2]<-"Brasil"

Demais_br <- t(data.frame(colSums(data_br_cases[c("AC","SE","AL","TO"),])))
rownames(Demais_br)[1]<-"Demais"

data_br_cases <- rbind(data_br_cases, Demais_br)


 Selectedstate_br <- c("Brasil"
                       ,"SP"
                       ,"RJ"
                       ,"CE"
                       ,"MG"
                       ,"RS"
                       ,"DF"
                       ,"PR"
                       ,"BA"
                       ,"AM"
                       ,"SC"
                       ,"RN"
                       ,"PE"
                       ,"ES"
                       ,"MA"
                       ,"GO"
                       ,"PA"
                       ,"MS"
                       ,"MT"
                       ,"Demais")



N = ncol(data_br_cases)

DT::datatable(data_br_cases[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')



 

 
 


  
```


Column {data-width=350}
-----------------------------------------------------------------------

### New Cases
```{r}

dife_c_br<-data_br_cases[, -1, drop = FALSE] - data_br_cases[, -ncol(data_br_cases), drop = FALSE]

N = ncol(dife_c_br)
DT::datatable(dife_c_br[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```


Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}

porce_c_br<-round(((data_br_cases[, -1, drop = FALSE] - data_br_cases[, -ncol(data_br_cases), drop = FALSE])/data_br_cases[, -ncol(data_br_cases), drop = FALSE]*100),2)

N = ncol(porce_c_br)
DT::datatable(porce_c_br[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
```



Deaths {data-navmenu='Brasil'} 
==========================================================================


Column {data-width=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}

data_br_deaths<-reshape(data_br, v.names = "deaths", idvar="state", direction = "wide", timevar = "date", drop=c("city","country","totalCases","newCases"))




date_br_deaths <- vapply(strsplit(colnames(data_br_deaths)[-1], "deaths."), '[', character(1), 2) %>% as.Date

colnames(data_br_deaths) <- c("state" ,format(date_br_deaths,"%m/%d/%y"))
rownames(data_br_deaths) <- data_br_deaths[,1]
data_br_deaths <- data_br_deaths[,-1]
rownames(data_br_deaths)[2]<-"Brasil"

Demais_br_d <- t(data.frame(colSums(data_br_deaths[c("AC","SE","AL","TO"),])))
rownames(Demais_br_d)[1]<-"Demais"

data_br_deaths <- rbind(data_br_deaths, Demais_br_d)






N = ncol(data_br_deaths)
DT::datatable(data_br_deaths[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')
  

```

Column {data-width=350}
-----------------------------------------------------------------------

### New Deaths
```{r}


dife_d_br<-data_br_deaths[, -1, drop = FALSE] - data_br_deaths[, -ncol(data_br_deaths), drop = FALSE]

N = ncol(dife_d_br)
DT::datatable(dife_d_br[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE))%>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')


```

Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}


porce_d_br<-round(((data_br_deaths[, -1, drop = FALSE] - data_br_deaths[, -ncol(data_br_deaths), drop = FALSE])/data_br_deaths[, -ncol(data_br_deaths), drop = FALSE]*100),2)

N = ncol(porce_d_br)
DT::datatable(porce_d_br[Selectedstate_br,(N-4):N],options = list(
  pageLength = 20,paging = FALSE,searching = FALSE)) %>%  DT::formatStyle(columns = 0:N, fontSize = '18pt')

```
















Graficos Selecionados
======================================================================

```{r}
xtsDates <- seq.Date(from       = as.Date('2020-01-22'),
                     length.out = ncol(data_wc) - 4,
                     by         = 'day')

cts <- xts(log10(do.call(cbind, Cases) + 1), xtsDates)
dts <- xts(log10(do.call(cbind, Death) + 1), xtsDates)

countriesAsia     <- c("China", "Japan", "Singapore", "Korea, South")
valuesAsia        <- round(10**(tail(cts[,countriesAsia], 1)) - 1, 0)
dvaluesAsia       <- round(10**(tail(dts[,countriesAsia], 1)) - 1, 0)

countriesEUR      <- c("Germany", "Italy", "France", "Spain")
valuesEUR         <- round(10**(tail(cts[,countriesEUR], 1)) - 1, 0)
dvaluesEUR        <- round(10**(tail(dts[,countriesEUR], 1)) - 1, 0)

countriesAmerica  <- c("Mexico", "Brazil", "US")
valuesAmerica     <- round(10**(tail(cts[,countriesAmerica], 1)) - 1, 0)
dvaluesAmerica    <- round(10**(tail(dts[,countriesAmerica], 1)) - 1, 0)
```

Column {data-width=300}
-----------------------------------------------------------------

### Asia Casos. `r vapply(countriesAsia, function(country) paste0(country, ": ", valuesAsia[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(cts[,countriesAsia], colorset = unname(lcolors[countriesAsia])) %>% dyRangeSelector(height = 10) 
```

### Europe Casos. `r vapply(countriesEUR, function(country) paste0(country, ": ", valuesEUR[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(cts[,countriesEUR], colorset = unname(lcolors[countriesEUR])) %>% dyRangeSelector(height = 10) 
```

### America Casos. `r vapply(countriesAmerica, function(country) paste0(country, ": ", valuesAmerica[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(cts[,countriesAmerica], colorset = unname(lcolors[countriesAmerica])) %>% dyRangeSelector(height = 10) 
```

Column {data-width=300}
-----------------------------------------------------------------

### Asia Mortes. `r vapply(countriesAsia, function(country) paste0(country, ": ", dvaluesAsia[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(dts[,countriesAsia], colorset = unname(lcolors[countriesAsia])) %>% dyRangeSelector(height = 10) 
```

### Europe Mortes. `r vapply(countriesEUR, function(country) paste0(country, ": ", dvaluesEUR[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(dts[,countriesEUR], colorset = unname(lcolors[countriesEUR])) %>% dyRangeSelector(height = 10) 
```

### America Mortes. `r vapply(countriesAmerica, function(country) paste0(country, ": ", dvaluesAmerica[,country]), character(1)) %>% as.vector()`
```{r}
chart.fl(dts[,countriesAmerica], colorset = unname(lcolors[countriesAmerica])) %>% dyRangeSelector(height = 10) 
```

Test 1 {data-navmenu='Graphics'} 
========================================================

Row {.tabset}
---------------------------------------------------------

### America (Cases)
```{r, fig.width = 10, fig.height = 5}

# Data frame with deaths
df = data.frame(coredata(10**(dts[,countriesAmerica] - 1)), index(dts[,countriesAmerica]))
colnames(df) <- c(countriesAmerica, 'date')

# Data frame with cases
cf = data.frame(coredata(10**(cts[,countriesAmerica] - 1)), index(cts[,countriesAmerica]))
colnames(cf) <- c(countriesAmerica, 'date')

f1 <- list(family = 'Old Standard TT, serif', size = 14, color = 'black')

c_axis <- list(
    title = "Cases (Log scale)",
    titlefont = f1,
    showticklabels = TRUE
)

x_axis <- list(
    title = "Days",
    titlefont = f1,
    showticklabels = TRUE
)

clr       <- lcolors[c(1,3,4)]
names(clr) <- countriesAmerica

fig <- plot_ly(cf, x = ~date)
for (country in countriesAmerica) {
 fig <- fig %>% add_trace(y = as.formula(paste0('~', country)), 
                          name = country,
                          mode = 'markers',
                          marker = list(color = unname(clr[country]), size = 10)) 
}
fig <- fig %>% layout(xaxis = x_axis, yaxis = c_axis)
fig
```

### America (Deaths)
```{r}
tp <- tail(df, 5)

p <- plot_ly()
for(country in countriesAmerica) {
  p <- p %>% add_trace(data = tp, x = ~date, y = as.formula(paste0('~', country)), name = country, type = 'bar', marker = list(color = unname(clr[country])))
}

xax <- list(
  title = 'Days',
  titlefont = f1,
  showticklabels = TRUE
)

yax <- list(
  title = 'Reported deaths',
  titlefont = f1,
  showticklabels = TRUE
)

p %>% layout(xaxis = xax, yaxis = yax)
```

Row {.tabset}
---------------------------------------------------------

### Asia (Cases)
```{r, fig.width = 10, fig.height = 5}

# Data frame with deaths
df = data.frame(coredata(10**(dts[,countriesAsia] - 1)), index(dts[,countriesAsia]))
colnames(df) <- c(countriesAsia, 'date')

# Data frame with cases
cf = data.frame(coredata(10**(cts[,countriesAsia] - 1)), index(cts[,countriesAsia]))
colnames(cf) <- c(countriesAsia, 'date')

f1 <- list(family = 'Old Standard TT, serif', size = 14, color = 'black')

c_axis <- list(
    title = "Cases",
    titlefont = f1,
    showticklabels = TRUE
)

x_axis <- list(
    title = "Days",
    titlefont = f1,
    showticklabels = TRUE
)

clr        <- lcolors[c(1,3,4)]
names(clr) <- rev(countriesAsia[1:3])

fig <- plot_ly(cf, x = ~date)
for (country in countriesAsia[1:3]) {
 fig <- fig %>% add_trace(y = as.formula(paste0('~', country)), 
                          name = country,
                          mode = 'markers',
                          marker = list(color = unname(clr[country]), size = 10)) 
}
fig <- fig %>% layout(xaxis = x_axis, yaxis = c_axis)
fig
```

### Asia (Deaths)
```{r}
tp <- tail(df, 5)

p <- plot_ly()
for(country in rev(countriesAsia[1:3])) {
  p <- p %>% add_trace(data = tp, x = ~date, y = as.formula(paste0('~', country)), name = country, type = 'bar', marker = list(color = unname(clr[country])))
}

xax <- list(
  title = 'Days',
  titlefont = f1,
  showticklabels = TRUE
)

yax <- list(
  title = 'Reported deaths',
  titlefont = f1,
  showticklabels = TRUE
)

p %>% layout(xaxis = xax, yaxis = yax)
```

Grafico copiado
========================================================

### Graphic 1
```{r, fig.width = 10, fig.height = 7}
countries <- c("Italy", "Spain", "France", "Germany", "US", "Brazil")

ects <- 10**(cts) - 1
d0ts <- ects * apply(ects, 2, function(x) x >= 100)
ld0ts <- lapply(countries, function(n) as.vector(coredata(d0ts[,n])))
ld0ts <- lapply(ld0ts, function(x) x[x!=0])
names(ld0ts) <- countries

N = max(vapply(ld0ts, length, numeric(1)))

d0f <- rbind(as.data.frame(lapply(ld0ts, '[', 1)), as.data.frame(lapply(ld0ts, '[', 2)))
for (i in 3:N) {
   d0f <- rbind(d0f, as.data.frame(lapply(ld0ts, '[', i)))
}

d0f <- cbind(1:N, d0f)
colnames(d0f) <- c('Days', countries)

p <- plot_ly(d0f, x = ~Days)
for (country in countries) {
    p <- p %>% add_trace(data = d0f, y = as.formula(paste0("~", country)), name = country, type = 'scatter', mode = 'lines+markers')
}

xax <- list(
  title = 'Days from D0',
  titlefont = f1,
  showticklabels = TRUE,
  range = c(0.5, 45),
  size = 13
)

yax <- list(
  title = 'Confirmed cases',
  titlefont = f1,
  showticklabels = TRUE,
  type = "log",
  size = 50
)

leg <- list(
  orientation = 'h',
  y = -0.15,
  x = 0.33
  )
p <- p %>% layout(xaxis = xax, yaxis = yax, legend = leg)



p
```

Bla
====================================================================
```{r, fig.height = 7, fig.width = 6}
countries <- c("Italy", "Spain", "Brazil")

ects <- 10**(cts) - 1
d0ts <- ects * apply(ects, 2, function(x) x >= 100)
ld0ts <- lapply(countries, function(n) as.vector(coredata(d0ts[,n])))
ld0ts <- lapply(ld0ts, function(x) x[x!=0])
names(ld0ts) <- countries

N = max(vapply(ld0ts, length, numeric(1)))

d0f <- rbind(as.data.frame(lapply(ld0ts, '[', 1)), as.data.frame(lapply(ld0ts, '[', 2)))
for (i in 3:N) {
   d0f <- rbind(d0f, as.data.frame(lapply(ld0ts, '[', i)))
}

daysToDouble <- c(2,4,7)
exdf <- NULL
for (i in daysToDouble) {
     exdf <- cbind(exdf, vapply(seq(ceiling(i*log(100, 2)), length.out = N), function(d) 2**(d/i), numeric(1)))
}

d0f <- cbind(d0f, exdf)
d0f <- log(d0f, 2)
d0f <- cbind(1:N, d0f)
DD  <- paste0("D", daysToDouble, "D")
colnames(d0f) <- c('Days', countries, DD)

p <- plot_ly(d0f, x = ~Days)
for (country in countries) {
    p <- p %>% add_trace(data = d0f, y = as.formula(paste0("~", country)), name = country, type = 'scatter', mode = 'lines+markers')
}

for (days in DD) {
  p <- p %>% add_lines(data = d0f, y = as.formula(paste0('~', days)), name = days, 
                       line = list(color = 'rgb(205, 12, 24)', dash = 'dot', width = 1),
                       showlegend = FALSE)
}

xax <- list(
  title = 'Days from D0',
  titlefont = f1,
  showticklabels = TRUE,
  range = c(0.5, 45),
  size = 13
)

yax <- list(
  title = 'Confirmed cases',
  titlefont = f1,
  showticklabels = TRUE,
#  type = "log",
  size = 50
)

leg <- list(
  orientation = 'h',
  y = -0.15,
  x = 0.42
  )

D1DA <- list(
  xref = 'paper',
  yref = 'y',
  x = 0.915,
#  y = tail(d0f,1)[,'D1D'],
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every day",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

D2DA <- list(
  xref = 'paper',
  yref = 'y',
  x = 0.915,
  y = tail(d0f,1)[,'D2D'],
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 2 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

D4DA <- list(
  xref = 'paper',
  yref = 'y',
  x = 0.915,
  y = tail(d0f,1)[,'D4D'],
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 4 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

D7DA <- list(
  xref = 'paper',
  yref = 'y',
  x = 0.915,
  y = tail(d0f,1)[,'D7D'],
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 7 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

p <- p %>% layout(xaxis = xax, yaxis = yax, legend = leg)
#p <- p %>% layout(annotations = D1DA)
p <- p %>% layout(annotations = D2DA)
p <- p %>% layout(annotations = D4DA)
p <- p %>% layout(annotations = D7DA)

p
```














