---
title: "Covid-19"
output: 
  flexdashboard::flex_dashboard:
    css: style.css
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(magrittr)
library(xts)
library(plotly)
library(dplyr)
library(formattable)

# hex msafra: #4c1211
# rgb msafra: 761817

gcal <- c("#039be5", "#7986cb", "#33b679", "#8e24aa", "#e67c73", "#f6c026", "#f5511d",	"#039be5", "#616161", "#3f51b5", "#0b8043", "#d60000")
ncal <- c('#5484ed','#a4bdfc','#46d6db', '#7ae7bf', '#51b749', '#fbd75b', '#ffb878', '#ff887c', '#dc2127', '#dbadff', '#e1e1e1')
hcal <- c('#f2aa0e', '#aa1717', '#3d8e53', '#3d8e72')

lcolors <- c("#000000"
            ,"#d0cece"
            ,"#7f7f7f"
            ,"#4c1211"
            ,"#007c00"
            ,"#ff0000"
            ,"#ffc000"
            ,"#00b050"
            ,"#f8dddc"
            ,"#bfe4ff"
            ,"#ffff00"
            ,"#bbffda")

names(lcolors) <- c("China", "Japan", "Singapore", "Korea, South", "Germany", "Italy", "France", "Spain", "Mexico", "Brazil", "US")

#========================================
# This is bold blue: '#5484ed'
# This is blue: '#a4bdfc'
# This is turquoise: '#46d6db'
# This is green: '#7ae7bf'
# This is bold green: '#51b749'
# This is yellow:'#fbd75b'
# This is orange: '#ffb878'
# This is red: '#ff887c'
# This is bold red: '#dc2127'
# This is purple: '#dbadff'
# This is gray: '#e1e1e1'
#=======================================
# This is unknown: '#039be5'
# This is Lavender: '#7986cb' 
# This is Sage: '#33b679'     
# This is Grape: '#8e24aa'
# This is Flamingo:	'#e67c73'
# This is Banana:	'#f6c026'
# This is Tangerine: '#f5511d'
# This is Peacock: '#039be5'
# This is Graphite:	'#616161'
# This is Bluberry:	'#3f51b5'
# This is Basil: '#0b8043'
# This is Tomato:	'#d60000'
#=======================================
# This is orange: '#f2aa0e'
# This is dark red: '#aa1717'
# This is green: '#3d8e53'
# This is water green: '#3d8e72'

plot.fl <- function(ts, title = '', colorset = c(gcal[1], ncal[7])) {
    require(PerformanceAnalytics)
    chart.TimeSeries(ts, main = title, colorset = colorset, legend.loc = 'topleft')
}

chart.fl <- function(ts, title = '', colorset = c(gcal[1],ncal[7])) {
    require(dygraphs)
    dygraph(ts, main = title, group = 'master') %>% 
    dyOptions(colors = colorset, axisLineWidth = .5, gridLineColor = 'lightgray') %>%
    #dyRangeSelector(height = 10, strokeColor = '') %>%
    dyHighlight(highlightSeriesBackgroundAlpha = 0.8) %>%
    dyLegend(show = 'auto', width = 550, hideOnMouseOut = TRUE)
}
```

Todos os Países
======================================================================

Column {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Evolução de Casos Países
```{r}
download <- RCurl::getURL("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")

# Watch out the time of updating
dias <- round(difftime(Sys.Date(), "2020-01-22", units = "days"), 0) + 5  

data_wc <- read.csv(text = download, 
                   stringsAsFactors = FALSE, 
                   colClasses = c(rep('character', 4), rep('numeric', dias - 4)))

dates <- colnames(data_wc)[-c(1:4)] %>% 
         strsplit(., 'X') %>% 
         lapply(., '[', 2) %>% 
         unlist() %>% 
         as.Date(format = "%m.%d.%y")
colnames(data_wc) <- c(colnames(data_wc)[1:4], format(dates, '%m/%d/%y'))

Countries_wc <- unique(data_wc[,2])
Cases <- list()
for (i in 1:length(Countries_wc)) {
    Cases[[i]] <- filter(data_wc, Country.Region == Countries_wc[i])[,-c(1:4)]  %>% colSums()  %>% as.vector()
}
names(Cases) <- Countries_wc

NewData_wc <- t(do.call(cbind, Cases))
colnames(NewData_wc) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wc)
DT::datatable(NewData_wc[,(N-4):N], 
              options = list(order = list(list(5, 'desc'))
))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Total de Mortos
```{r}
download <- RCurl::getURL("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv")

data_wd <- read.csv(text = download, 
                 stringsAsFactors = FALSE, 
                 colClasses = c(rep('character', 4), rep('numeric', dias-4)))

Countries_wd <- unique(data_wd[,2])
Death <- list()
for (i in 1:length(Countries_wd)) {
    Death[[i]] <- filter(data_wd, Country.Region == Countries_wd[i])[,-c(1:4)]  %>% colSums()  %>% as.vector()
}
names(Death) <- Countries_wd

NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wd)
DT::datatable(NewData_wd[,(N-4):N], 
              options = list(order = list(list(5, 'desc'))
))

```


Cases {data-navmenu='Europa'} 
==========================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### Total Cases
```{r}
SelectedCountries <- c("Italy"
                      ,"Spain"
                      ,"Germany"
                      ,"France"
                      ,"United Kingdom"
                      ,"Switzerland"
                      ,"Belgium"
                      ,"Netherlands"
                      ,"Austria"
                      ,"Portugal"
                      ,"Sweden"
                      ,"Norway"
                      ,"Denmark"
                      ,"Ireland"
                      ,"Romania"
                      ,"Luxembourg"
                      ,"Finland"
                      ,"Greece"
                      ,"Poland"
                      ,"Kosovo")


N = ncol(NewData_wc)
DT::datatable(NewData_wc[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))
```

Column {data-width=350}
-----------------------------------------------------------------------

### New Cases
```{r}

dife_c<-NewData_wc[, -1, drop = FALSE] - NewData_wc[, -ncol(NewData_wc), drop = FALSE]

N = ncol(dife_c)
DT::datatable(dife_c[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))
```


Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}

porce_c<-round(((NewData_wc[, -1, drop = FALSE] - NewData_wc[, -ncol(NewData_wc), drop = FALSE])/NewData_wc[, -ncol(NewData_wc), drop = FALSE]*100),2)

N = ncol(porce_c)
DT::datatable(porce_c[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))
```



Deaths {data-navmenu='Europa'} 
==========================================================================


Column {data-width=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

N = ncol(NewData_wd)
DT::datatable(NewData_wd[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))

```

Column {data-width=350}
-----------------------------------------------------------------------

### New Deaths
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")



dife_d<-NewData_wd[, -1, drop = FALSE] - NewData_wd[, -ncol(NewData_wd), drop = FALSE]

N = ncol(dife_d)
DT::datatable(dife_d[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))


```

Column {data-width=350}
-----------------------------------------------------------------------

### Var. (%)
```{r}
NewData_wd <- t(do.call(cbind, Death))
colnames(NewData_wd) <- format(dates, "%m/%d/%y")

porce_d<-round(((NewData_wd[, -1, drop = FALSE] - NewData_wd[, -ncol(NewData_wd), drop = FALSE])/NewData_wd[, -ncol(NewData_wd), drop = FALSE]*100),2)

N = ncol(porce_d)
DT::datatable(porce_d[SelectedCountries,(N-4):N],options = list(
  pageLength = 20))

```






Graficos Selecionados
======================================================================

```{r}
xtsDates <- seq.Date(from       = as.Date('2020-01-22'),
                     length.out = ncol(data_wc) - 4,
                     by         = 'day')

cts <- xts(log(do.call(cbind, Cases) + 0.05), xtsDates)
dts <- xts(log(do.call(cbind, Death) + 0.05), xtsDates)
```

Column {data-width=300}
-----------------------------------------------------------------
### Asia (Casos)
```{r}
cty         <- c("China", "Japan", "Singapore", "Korea, South")
chart.fl(cts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

### Europe (Casos)
```{r}
cty         <- c("Germany", "Italy", "France", "Spain")

chart.fl(cts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

### America (Casos)
```{r}
cty         <- c("Mexico", "Brazil", "US")

chart.fl(cts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

Column {data-width=300}
-----------------------------------------------------------------
### Asia (Mortes)
```{r}
cty         <- c("China", "Japan", "Singapore", "Korea, South")

chart.fl(dts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

### Europe (Mortes)
```{r}
cty         <- c("Germany", "Italy", "France", "Spain")

chart.fl(dts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

### America (Mortes)
```{r}
cty         <- c("Mexico", "Brazil", "US")

chart.fl(dts[,cty], colorset = unname(lcolors[cty])) %>% dyRangeSelector(height = 5)
```

Test 1 {data-navmenu='Graphics'} 
========================================================

Column {.tabset}
---------------------------------------------------------

### America (Cases)
```{r, fig.width = 10, fig.height = 5}
lC = c('US', 'Mexico', 'Brazil')

df = data.frame(coredata(dts[,lC]), index(dts[,lC]))
colnames(df) <- c(lC, 'date')

cf = data.frame(log(coredata(cts[,lC])), index(cts[,lC]))
colnames(cf) <- c(lC, 'date')

f1 <- list(family = 'Old Standard TT, serif', size = 14, color = 'black')

c_axis <- list(
    title = "Number of Cases (Log scale)",
    titlefont = f1,
    showticklabels = TRUE
)

x_axis <- list(
    title = "Dates",
    titlefont = f1,
    showticklabels = TRUE
)

fig <- plot_ly(cf, x = ~date)
for (country in lC) {
 fig <- fig %>% add_trace(y = as.formula(paste0('~', country)), 
                          name = country,
                          mode = 'markers') 
}
fig <- fig %>% layout(xaxis = x_axis, yaxis = c_axis)
fig
```

### America (Deaths)
```{r}
p <- plot_ly(type='bar', x = lC, y = as.numeric(tail(df[,-4],1)))
p
```

Test 2 {data-navmenu='Graphics'} 
========================================================

### Plotly Version
```{r}


df = data.frame(coredata(dts[,lC]), index(dts[,lC]))
colnames(df) <- c(lC, 'date')

cf = data.frame(coredata(cts[,lC]), index(cts[,lC]))
colnames(cf) <- c(lC, 'date')

plots <- lapply(lC, function(var) {
  plot_ly(cf, x = ~date, y = as.formula(paste0("~", var))) %>%
    add_lines(name = var)
})
subplot(plots, nrows = length(plots), shareX = TRUE, titleX = FALSE)
```



Grafico copiado
========================================================

### Graphic 1
```{r, fig.width = 10, fig.height = 7}
countries <- c("Italy", "Spain", "France", "Germany", "US", "Brazil")

ects <- 10**(cts) - 1
d0ts <- ects * apply(ects, 2, function(x) x >= 100)
ld0ts <- lapply(countries, function(n) as.vector(coredata(d0ts[,n])))
ld0ts <- lapply(ld0ts, function(x) x[x!=0])
names(ld0ts) <- countries

N = max(vapply(ld0ts, length, numeric(1)))

d0f <- rbind(as.data.frame(lapply(ld0ts, '[', 1)), as.data.frame(lapply(ld0ts, '[', 2)))
for (i in 3:N) {
   d0f <- rbind(d0f, as.data.frame(lapply(ld0ts, '[', i)))
}

d0f <- cbind(1:N, d0f)
colnames(d0f) <- c('Days', countries)

p <- plot_ly(d0f, x = ~Days)
for (country in countries) {
    p <- p %>% add_trace(data = d0f, y = as.formula(paste0("~", country)), name = country, type = 'scatter', mode = 'lines+markers')
}

xax <- list(
  title = 'Days from D0',
  titlefont = f1,
  showticklabels = TRUE
)

yax <- list(
  title = 'Confirmed cases',
  titlefont = f1,
  showticklabels = TRUE,
  type = "log"
)

p <- p %>% layout(xaxis = xax, yaxis = yax)

#htmlwidgets::saveWidget(p, file = "/home/henrique/Documents/Padulla/corona_dash/graph.html")

p
```
