---
title: "Covid-19"
output: 
  flexdashboard::flex_dashboard:
    css: style.css
    orientation: rows
    vertical_layout: scroll
  rmarkdown:: github_document
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(sidrar)
library(xlsx)
library(RSelenium)


# Some color schemes: 

# hex msafra: #4c1211
# rgb msafra: 761817
plotlyColors <-   c('#740001',
                    '#005b96',
                    '#23272a',
                    '#d3a625',
                    '#008744',
                    '#fb2e01',
                    '#01cdfe',
                    '#99aab5',
                    '#ffc425',
                    '#00b159',
                    '#d11141',
                    '#00aedb',
                    '#777777',
                    '#ffe28a',
                    '#6fcb9f',
                    '#0057e7',
                    '#ae0001',
                    '#05ffa1',
                    '#b967ff',
                    '#7289da',
                    '#f37735',
                    '#666547',
                    '#d62d20',
                    '#6497b1',
                    '#b3cde0',
                    '#ff4d00',
                    '#66545e',
                    '#a39193',
                    '#aa6f73',
                    '#eea990'
                    )




 
# Setting time span: Watch out the time of updating
dias <- ceiling(difftime(Sys.Date(), "2020-01-22", units = "days")) #-1

# Choose here the path to output png plots:
ggpath  <- "C:/Users/Padulla/Documents/GitHub/corona_dash/"
Here    <- Sys.Date()
HereUSA <- Here - 0
HereBR  <- Here - 0

# loading stuff
source("Functions.R")
source("World.R")
source("USA.R")
source("Brazil.R")


# Reading country codes for map plot. 
WorldCodes <- read_csv(file = "../worldCodes.csv"
                      ,col_names = TRUE
                      ,col_types = 'cc')

USACodes <-read_csv(file = "../usaCodes.csv"
                   ,col_names = TRUE
                   ,col_types = 'cc')
```

Overview {data-navmenu='World'}
======================================================================

Row {data-width = 800, data-height = 100}
-----------------------------------------

### World Cases {.no-title}
```{r, fig.width = 10, fig.height = 7}
# MAGIC TIME! Joinining dataframes by country and filling the NA with 0

dg <- WorldCases %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("COUNTRY", "CASES")) %>% 
        left_join(WorldCodes, ., by = 'COUNTRY') %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

plotMap(dg, 'world', "Worldwide COVID-19 Cases")
```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Total Cases </b>
```{r}
tableWorldCases
```

### <b style = "color: #4c1112" > Total Deaths </b>
```{r}
tableWorldDeaths
```

Mortality {data-navmenu='World'}
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112"> Mortality Rate </b>
```{r, fig.height = 6, fig.width = 10}
WorldCountries <- c("United States"
                   ,"Italy"
                   ,"Spain"
                   ,"France"
                   ,"United Kingdom"
                   #,"Iran"
                   ,"China"
                   ,"Germany"
                   ,"Netherlands"
                   ,"Brazil")

plotMortality(WorldMortality, WorldCountries, "Mortality Rate by Country")
```

### <b style = "color: #4c1112">  Daily variation of Mortality </b>
```{r, fig.height = 6, fig.width = 10}
dx <- 
WorldMortality %>% 
  mutate_at(vars(-Dates), ~ . - lag(.)) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% 
  mutate_at(vars(-Dates), ~ round(., 2))

plotMortality(WorldMortality, WorldCountries, "Mortality Variation")
```

Cases {data-navmenu='Europe'} 
==========================================================================

Column 
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative after 100 cases </b>
```{r, fig.width = 10, fig.height = 6}
countries <- c("Italy", "Spain", "France", "Germany", "United Kingdom", "Netherlands")
plots <- plotThis(WorldCases, countries, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plots$plotly
ggsave(paste0(ggpath, "1EuropeCases.png"))
```

### <b style = "color: #4c1112" > Europe: Total Cases </b>
```{r, fig.width = 10, fig.height = 6, fig.align = 'right'}
## MAGIC TIME! Joinining dataframes by country and filling the NA with 0
dg <- WorldCases %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("COUNTRY", "CASES")) %>% 
        left_join(WorldCodes, ., by = 'COUNTRY') %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

plotMap(dg, 'europe', "Europe COVID-19 Cases")
```

Column {data-width=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Total Cases </b>
```{r}
printDT(WorldCases, 
        SelectedCountries
       )
```


### <b style = "color: #4c1112" > New Cases </b>
```{r}
printDT(dife_c, 
        SelectedCountries
       ) 
```

### <b style = "color: #4c1112" > Var (%) </b>
```{r}
printDT(porce_c / 100, 
        SelectedCountries
      ) %>% DT::formatPercentage(1:5, 2)
```



Cases per day Graphs {data-navmenu='Europe'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Cases per day
```{r, fig.width = 10, fig.height = 12}



ListOfCountries <- 
WorldCases %>% 
       rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna) %>%
       filter(NovaColuna %in% SelectedCountries) %>% pull()


dz <- 
WorldCases %>% 
  t %>% 
  as_tibble %>% 
  select(ListOfCountries) %>%
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(WorldCases), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))



dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-01"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:21], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                          t <- dh[nrow(dh),x]
                          tt <- WorldCases[x,ncol(WorldCases)]
                           a <- list(
                                      text = paste0(x," - Total Cases:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p

#export_plotly2SVG(p, filename = "happyplot.svg", parent_path = getwd())
```



Doubling Time {data-navmenu='Europe'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}


doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}

da <- 
WorldCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(all_of(SelectedCountries)) %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(DatesWorld)) %>% 
  filter(Days >= as.Date("2020-03-02"))

gg <- ggplot(da, aes(x = Days)) 
for (i in SelectedCountries) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = countries)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
##ggsave(paste0(ggpath, "DoublingTime.png"))
```




Deaths {data-navmenu='Europe'} 
==========================================================================

Column 
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative After 100 deaths </b>
```{r, fig.width = 10, fig.height = 6}
countries <- c("Italy", "Spain", "France", "Germany", "United Kingdom", "Netherlands")
plots <- plotThis(WorldDeaths, countries, ytitle = "Confirmed Deaths", xtitle = "Days from 100 Deaths")
plots$plotly
##ggsave(paste0(ggpath, "2EuropeDeaths.png"))
```

### <b style = "color: #4c1112">  Europe: total deaths </b>
```{r, fig.width = 10, fig.height = 6, fig.align = 'right'}
## MAGIC TIME! Joinining dataframes by country and filling the NA with 0
dg <- WorldDeaths %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("COUNTRY", "CASES")) %>% 
        left_join(WorldCodes, ., by = 'COUNTRY') %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

plotMap(dg, 'europe', "Europe COVID-19 Deaths")
```

Column {data-width=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Total Deaths </b>
```{r}
printDT(WorldDeaths,
        SelectedCountries
       )
```


### <b style = "color: #4c1112" > New Deaths </b>
```{r}
printDT(dife_d, 
        SelectedCountries
       )
```


### <b style = "color: #4c1112" > Var (%) </b>
```{r}
printDT(porce_d / 100, 
        SelectedCountries
       ) %>% DT::formatPercentage(1:5, 2)
```


Deaths per day Graphs {data-navmenu='Europe'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Deaths per day
```{r, fig.width = 10, fig.height = 12}
ListOfCountries <- 
WorldCases %>% 
       rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna) %>%
       filter(NovaColuna %in% SelectedCountries) %>% pull()





dz <- 
WorldDeaths %>% 
  
  t %>% 
  as_tibble %>% 
  select(ListOfCountries) %>%
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(WorldDeaths), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-01"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:21], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- WorldDeaths[x,ncol(WorldDeaths)]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```






Mortality {data-navmenu='Europe'}
=========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112"> Mortality Rate </b>
```{r, fig.height = 6, fig.width = 10}
plotMortality(WorldMortality, countries, "Europe Mortality Rate")
```

### <b style = "color: #4c1112">  Daily variation of Mortality </b>
```{r, fig.height = 6, fig.width = 10}
plotMortality(dx, countries, "Europe Mortality Variation")
```

Cases {data-navmenu='US'} 
==========================================================================

Column 
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative After 100 cases </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("New York", "New Jersey", "Michigan", "California", "Massachussets", "Florida", "Washington", "Texas")
abr    <- c("NY", "NJ", "MI", "CA", "MA", "FL", "WA", "TX")
 
plot <- plotThis(UsCases, states, abr, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plot$plotly
ggsave(paste0(ggpath, "3USACases.png"))
```

### <b style = "color: #4c1112">  USA: total cases </b>
```{r, fig.width = 10, fig.height = 6, fig.align = 'right'}
## MAGIC TIME! Joinining dataframes by country and filling the NA with 0
dg <- UsCases %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("code", "CASES")) %>% 
        left_join(USACodes, ., by = 'code') %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% 
        rename_at(vars(code, state), ~ c("CODE", "COUNTRY"))

plotMap(dg, 'usa', "USA COVID-19 Cases", proj = "albers usa")
```

Column {data-width=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Total Cases </b>
```{r}
printDT(UsCasesFormatted, 
        rownames(UsCasesFormatted)
        )
```


### <b style = "color: #4c1112"> New Cases </b>
```{r}
printDT(dife_c_us,
        rownames(dife_c_us)
        )
```

### <b style = "color: #4c1112"> Var. (%) </b>
```{r}
printDT(porce_c_us / 100,
        rownames(porce_c_us)
        ) %>% DT::formatPercentage(1:5, 2)
```


Cases per day Graphs {data-navmenu='US'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Cases per day
```{r, fig.width = 5, fig.height = 30}
cols_names <- USACodes %>% rbind("US") 
dz <- 
  UsCases[-c(57), ]  %>%
  mutate(States = cols_names$state) %>%
  select(States, everything())
  rownames(dz) <- dz[,1]
  dz[,1] <- NULL
  
  
 dz <- dz %>% 
       rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna")
  
  

dzz <- t(dz) %>% 
  as_tibble %>% 
    mutate(Dates = as.Date(colnames(UsCases), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))  
  
  
  
  
  dz <- t(dz) %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(UsCases), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))



dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>%   
  filter(Dates >= as.Date("2020-03-01"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:58], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                          tt <- dzz[nrow(dzz),x]
                           maximum <- max(dh[,x])
                           data_reab <- DataReabertUS[1,x]

                          a <- list(
                                      text = paste0(x," - Total Cases:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                            add_segments(x = data_reab, xend = data_reab, y = 0, yend = maximum, color=I("red")) %>% 
                             layout(showlegend = FALSE, annotations = a)
})



names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 15, shareX = FALSE, shareY = FALSE)
p
```


<!-- HeatMaP Cases {data-navmenu='US'} -->
<!-- ==================================================================== -->



<!-- ### Moving Average of 7 days (Var. %) -->
<!-- ```{r, fig.width = 10, fig.height = 12} -->
<!-- df1 <- dz -->



<!-- # BrCases %>% -->
<!-- #   rownames_to_column(var = "NovaColuna") %>% -->
<!-- #   arrange_at(vars(last_col()), desc) %>% -->
<!-- #   select(NovaColuna, everything())  %>% -->
<!-- #   column_to_rownames("NovaColuna") %>% -->
<!-- #   t %>% -->
<!-- #   as_tibble %>% -->
<!-- #   mutate_all(~ . - lag(.)) %>% -->
<!-- #   mutate(Dates = as.Date(colnames(BrCases), format = "%m/%d/%y") ) %>% -->
<!-- #   select(Dates, everything()) %>% -->
<!-- #   mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) -->


<!-- estadosDF1 <- colnames(df1)[-1]  -->


<!-- df2 <- -->
<!--   do.call(cbind, lapply(colnames(df1)[-1], function(x) TTR::SMA(df1[,x], 7))) %>% -->
<!--   as_tibble %>% -->
<!--   mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% -->
<!--   mutate_all(., function(x) pct_change = (x/lag(x,n=7) - 1) * 100) %>% -->
<!--   mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% -->
<!--   t %>% -->
<!--   as_tibble %>% -->
<!--   mutate_all(., function(x) as.numeric(x)) %>% -->
<!--   round(2) %>% -->
<!--   cbind(estadosDF1) %>%  -->
<!--   as_tibble -->



<!-- colnames(df2) <- Dates -->

<!-- names(df2)[length(names(df2))]<-"space"  -->


<!-- m <- df2[1:28,] %>%   -->
<!--   column_to_rownames("space") %>% select(last_col(15:0)) %>% rownames_to_column() %>%   arrange_at(vars(last_col())) %>%  column_to_rownames("rowname") %>%  as.matrix() -->





<!--  p <- plot_ly(x=colnames(m), y=rownames(m), z = m, zmin=-50,zmax=100, zsmooth=FALSE, ygap =0.25,xgap =0.25, colorscale = "reds", type = "heatmap") #%>% add_annotations(text=m) -->
<!--  p -->


<!-- ``` -->
















Doubling Time {data-navmenu='US'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}
SelectedUS <- c( "US"
               ,"NY"
               ,"NJ"
               ,"MI"
               ,"CA"
               ,"MA"
               ,"FL"
               ,"IL"
               ,"LA"
               ,"WA"
               ,"PA"
               ,"GA"
               ,"TX"
               ,"CT"
               ,"CO"
               ,"TN"
               ,"OH"
               ,"IN"
               ,"MD")



doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}

Dates <- seq.Date(from = as.Date('2020-01-22'),
                  to   = HereUSA,
                  by   = 'day')

da <- 
UsCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(all_of(SelectedUS)) %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(Dates)) %>% 
  filter(Days >= as.Date("2020-03-02"))

gg <- ggplot(da, aes(x = Days)) 
for (i in SelectedUS) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = countries)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
##ggsave(paste0(ggpath, "DoublingTime.png"))
```

Hospitalized {data-navmenu='US'} 
==========================================================================

Column {data-width=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Total Hospitalized </b>
```{r}
printDT(UsHospFormatted, 
        rownames(UsHospFormatted)
        )
```


### <b style = "color: #4c1112"> Daily </b>
```{r}
printDT(dife_h_us,
        rownames(dife_h_us)
        )
```






Deaths {data-navmenu='US'} 
==========================================================================

Column 
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative After 100 cases </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("New York", "New Jersey", "Michigan", "California", "Massachussets", "Florida", "Washington", "Texas")
abr    <- c("NY", "NJ", "MI", "CA", "MA", "FL", "WA", "TX")

plot <- plotThis(UsCases, states, abr, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plot$plotly
##ggsave(paste0(ggpath, "4USADeaths.png"))
```

### <b style = "color: #4c1112">  USA: total deaths </b>
```{r, fig.width = 10, fig.height = 6, fig.align = 'right'}
## MAGIC TIME! Joinining dataframes by country and filling the NA with 0
dg <- UsDeaths %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("code", "CASES")) %>% 
        left_join(USACodes, ., by = 'code') %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))  %>% 
        rename_at(vars(code, state), ~ c("CODE", "COUNTRY"))

plotMap(dg, 'usa', "USA COVID-19 Deaths", proj = 'albers usa')
```


Column {data-width=350}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Total Deaths </b>
```{r}
printDT(UsDeathsFormatted, 
        rownames(UsDeathsFormatted)
        )
```


### <b style = "color: #4c1112"> New Deaths </b>
```{r}
printDT(dife_d_us,
        rownames(dife_d_us)
        )
```

### <b style = "color: #4c1112"> Var. (%) </b>
```{r}
printDT(porce_d_us / 100,
        rownames(porce_d_us)
        ) %>% DT::formatPercentage(1:5, 2)
```


Deaths per day Graphs {data-navmenu='US'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Deaths per day
```{r, fig.width = 10, fig.height = 30}
cols_names <- USACodes %>% rbind("US") 
dz <- 
  UsDeaths[-c(57), ]  %>%
  mutate(States = cols_names$state) %>%
  select(States, everything())
  rownames(dz) <- dz[,1]
  dz[,1] <- NULL


  
 dz <- dz %>% 
       rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna")  
  
  
  
    
  dzs <- t(dz) %>% 
  as_tibble %>% 
  mutate(Dates = as.Date(colnames(UsDeaths), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

  
  
  
  
  
  
  dz <- t(dz) %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(UsDeaths), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))



dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>%   
  filter(Dates >= as.Date("2020-03-01"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:58], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- dzs[nrow(dzz),x]
                           maximum <- max(dh[,x])
                           data_reab <- DataReabertUS[1,x]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             add_segments(x = data_reab, xend = data_reab, y = 0, yend = maximum, color=I("red")) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 15, shareX = FALSE, shareY = FALSE)
p
```




Mortality {data-navmenu="US"}
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112"> Mortality Rate </b>
```{r, fig.height = 6, fig.width = 10}
UsMortalityFormatted <-      
UsMortality %>% 
  select(Dates, abr) %>% 
  mutate_at(vars(-Dates), ~ round(., 2)) %>% 
  rename_at(vars(-Dates), ~ states) %>% 
  filter(Dates >= as.Date("2020-03-05"))

plotMortality(UsMortalityFormatted, states, "USA Mortality Rate by State")
```

### <b style = "color: #4c1112">  Daily variation of Mortality </b>
```{r, fig.height = 6, fig.width = 10}
dx <- 
UsMortalityFormatted %>% 
  mutate_at(vars(-Dates), ~ . - lag(.)) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% 
  mutate_at(vars(-Dates), ~ round(., 2))

plotMortality(dx, states, "USA Mortality Rate Variation by State")
```

Cases {data-navmenu='Brasil'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative after 100 cases </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

S_SE <- c("SP"
           ,"RJ"
           ,"MG"
           ,"RS"
           ,"PR"
           ,"SC"
           ,"ES"
           )


Norte <- c("AM"
           ,"PA"
           ,"AC"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"RR"
           )


CO <- c("DF"
        ,"GO"
           ,"MS"
           ,"MT"
           )

NE <- c("CE"
         ,"BA"
           ,"PE"
           ,"MA"
           ,"SE"
           ,"AL"
           ,"PB"
           ,"PI"
           ,"RR"
           )


plotN <- plotThis(BrCases, Norte, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotNE <- plotThis(BrCases, NE, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotS_SE <- plotThis(BrCases, S_SE, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotCO <- plotThis(BrCases, CO, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")


plot <- plotThis(BrCases, states, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")

# fig <- subplot(plotN$plotly, plotNE$plotly,plotCO$plotly,plotS_SE$plotly, nrows = 2, shareX = TRUE, shareY = FALSE, titleX = T, titleY = T)
# fig

plot$plotly

##ggsave(paste0(ggpath, "5BRCases.png"))

```

### <b style = "color: #4c1112" > Comparative after 10 cases per 100.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis10(BrCasesPop, states, ytitle = "Confirmed Cases", xtitle = "Days from 10 Cases")
plot$plotly
##ggsave(paste0(ggpath, "BRCasespop.png"))

```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Cases
```{r}
printDT(BrCasesFormatted,
        rownames(BrCasesFormatted)
        )
```

### New Cases
```{r}
printDT(dife_c_br,
        rownames(dife_c_br)
        )
```


### Var. (%)
```{r}
printDT(porce_c_br / 100,
        rownames(porce_c_br)
       ) %>% DT::formatPercentage(1:5, 2)
```


Cases per day Graphs {data-navmenu='Brasil'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Cases per day
```{r, fig.width = 10, fig.height = 12}
dz <- 
BrCases %>% 
  rownames_to_column(var = "NovaColuna") %>%
  arrange_at(vars(last_col()), desc) %>%
  select(NovaColuna, everything())  %>%
  column_to_rownames("NovaColuna") %>%
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrCases), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))




dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))







dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:29], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           maximum <- max(dh[,x])
                           data_reab <- DataReabertBR[1,x]
                           tt <- BrCases[x,ncol(BrCases)]
                           a <- list(
                                      text = paste0(x," - Total Cases:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                              add_segments(x = data_reab, xend = data_reab, y = 0, yend = maximum, color=I("red")) %>% 
                             layout(showlegend = FALSE, annotations = a)
                            
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```




HeatMaP Cases {data-navmenu='Brasil'}
====================================================================



### Moving Average of 7 days (Var. %)
```{r, fig.width = 10, fig.height = 12}
df1 <-
BrCases %>%
  rownames_to_column(var = "NovaColuna") %>%
  arrange_at(vars(last_col()), desc) %>%
  select(NovaColuna, everything())  %>%
  column_to_rownames("NovaColuna") %>%
  t %>%
  as_tibble %>%
  mutate_all(~ . - lag(.)) %>%
  mutate(Dates = as.Date(colnames(BrCases), format = "%m/%d/%y") ) %>%
  select(Dates, everything()) %>%
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))


estadosDF1 <- colnames(df1)[-1] 


df2 <-
  do.call(cbind, lapply(colnames(df1)[-1], function(x) TTR::SMA(df1[,x], 7))) %>%
  as_tibble %>%
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>%
  mutate_all(., function(x) pct_change = (x/lag(x,n=7) - 1) * 100) %>%
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>%
  t %>%
  as_tibble %>%
  mutate_all(., function(x) as.numeric(x)) %>%
  round(2) %>%
  cbind(estadosDF1) %>% 
  as_tibble



colnames(df2) <- Dates

names(df2)[length(names(df2))]<-"space" 


m <- df2[1:28,] %>%  
  column_to_rownames("space") %>% select(last_col(15:0)) %>% rownames_to_column() %>%   arrange_at(vars(last_col())) %>%  column_to_rownames("rowname") %>%  as.matrix()
 

 
 
 
 p <- plot_ly(x=colnames(m), y=rownames(m), z = m, zmin=-50,zmax=100, zsmooth=FALSE, ygap =0.25,xgap =0.25, colorscale = "reds", type = "heatmap") #%>% add_annotations(text=m)
 p


```











Doubling Time {data-navmenu='Brasil'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}
countries <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}


Dates <- seq.Date(from = as.Date('2020-02-25'),
                  to   = HereBR,
                  by   = 'day')


da <- 
BrCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(all_of(countries)) %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(Dates)) %>% 
  filter(Days >= as.Date("2020-03-02"))

gg <- ggplot(da, aes(x = Days)) 
for (i in countries) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = countries)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
##ggsave(paste0(ggpath, "DoublingTime.png"))
```




Deaths {data-navmenu='Brasil'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative after 100 deaths </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis(BrDeaths, states, ytitle = "Confirmed Deaths", xtitle = "Days from 100 Deaths")
plot$plotly
##ggsave(paste0(ggpath, "6BRDeaths.png"))

```


<!-- Column  -->
<!-- ----------------------------------------------------------------------- -->
### <b style = "color: #4c1112" > Comparative after 10 deaths per 1.000.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis10(BrDeathsPop, states, ytitle = "Confirmed Deaths", xtitle = "Days from 10 Deaths")
plot$plotly
##ggsave(paste0(ggpath, "BRDeathspop.png"))
```


### <b style = "color: #4c1112" > Comparative Official and States </b>
```{r, fig.width = 10, fig.height = 6}

dmb1 <- BrDeaths    %>%   t %>%   as_tibble  %>% select ('Brasil') %>% rename(BrasilS=Brasil)
dmb2 <- BrDeathsMS        %>% t  %>% as_tibble        %>% select ('Brasil') %>% rename(BrasilMS=Brasil)
dmb3 <- BrDeaths_dif        %>% t  %>% as_tibble        %>% select ('Brasil') %>% rename(BrasilD=Brasil)


dmb <- cbind(dmb1,dmb2)

dmb <- dmb %>% 
  as_tibble %>%        
  #mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>%   select(Dates, everything())  %>% 
  filter(Dates >= as.Date("2020-03-29"))

dmb3 <- dmb3 %>% 
  as_tibble %>%        
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>%   select(Dates, everything())  %>% 
  filter(Dates >= as.Date("2020-03-29"))




fig1 <- plot_ly(
  x = dmb$Dates,
  y = dmb$BrasilS,
   name = 'States',
  type = "bar",
  color = I("firebrick4")
) %>%
layout(
     title = "Official vs States",
     xaxis = list(title = "Date",
     categoryorder = "array",
     categoryarray = ~dmb$Dates),
     yaxis = list(title = "Deaths")
)

fig1 <- fig1 %>% add_trace(y = dmb$BrasilMS, name = 'Official',
  color = I("dimgrey"))






fig2 <- plot_ly(
  x = dmb3$Dates,
  y = dmb3$BrasilD,
   name = 'Dif.',
  type = "bar",
  color = I("dodgerblue4")
) %>%
layout(
     title = "Difference (States-Official)",
     xaxis = list(title = "Date",
     categoryorder = "array",
     categoryarray = ~dmb3$Dates),
     yaxis = list(title = "Deaths")
)







p <- subplot(fig1, fig2,  nrows = 2, shareX = FALSE, shareY = FALSE)
p





```


Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}
printDT(BrDeathsFormatted,
        rownames(BrDeathsFormatted)
       )
```


### New Deaths
```{r}
printDT(dife_d_br,
        rownames(dife_d_br)
      )
```


### Var. (%)
```{r}
printDT(porce_d_br / 100,
        rownames(porce_d_br)
       ) %>% DT::formatPercentage(1:5, 2)
```


Deaths per day Graphs {data-navmenu='Brasil'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### Deaths per day - States
```{r, fig.width = 10, fig.height = 12}
dz <- 
BrDeaths %>% 
  rownames_to_column(var = "NovaColuna") %>%
  arrange_at(vars(last_col()), desc) %>%
  select(NovaColuna, everything())  %>%
  column_to_rownames("NovaColuna") %>%
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:29], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- BrDeaths[x,ncol(BrDeaths)]
                           maximum <- max(dh[,x])
                           data_reab <- DataReabertBR[1,x]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>%
                             add_segments(x = data_reab, xend = data_reab, y = 0, yend = maximum, color=I("red")) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```

























### Deaths per day - Official MS
```{r, fig.width = 10, fig.height = 12}
dz <- 
BrDeathsMS %>% 
  rownames_to_column(var = "NovaColuna") %>%
  arrange_at(vars(last_col()), desc) %>%
  select(NovaColuna, everything())  %>%
  column_to_rownames("NovaColuna") %>%
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrDeathsMS), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:29], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- BrDeathsMS[x,ncol(BrDeathsMS)]
                           maximum <- max(dh[,x])
                           data_reab <- DataReabertBR[1,x]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>%
                             add_segments(x = data_reab, xend = data_reab, y = 0, yend = maximum, color=I("red")) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```






Tests {data-navmenu='Brasil'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Tests </b>
```{r, fig.width = 10, fig.height = 6}
tg <- BrTests %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("States", "Tests")) %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 
tg <-tg[-c(28,29), ] 
tg <- arrange(tg,desc(Tests))


  
fig <- plot_ly(
  x = tg$States,
  y = tg$Tests,
  type = "bar",
  color = I("Gray")
) %>%
layout(
     title = "Total Tests",
     xaxis = list(title = "States",
     categoryorder = "array",
     categoryarray = ~tg$States),
     yaxis = list(title = "Tests")
)

fig

```

### <b style = "color: #4c1112" > Tests 100.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
tg <- BrTestsP100k %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("States", "Tests")) %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 
tg <-tg[-c(28,29), ] 
tg <- arrange(tg,desc(Tests))


  
fig <- plot_ly(
  x = tg$States,
  y = tg$Tests,
  type = "bar",
  color = I("firebrick4")
) %>%
layout(
     title = "Total Tests per 100k hab.",
     xaxis = list(title = "States",
     categoryorder = "array",
     categoryarray = ~tg$States),
     yaxis = list(title = "Tests per 100k hab.")
)

fig

```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Tests
```{r}
printDT(BrTestsFormatted,
        rownames(BrTestsFormatted)
        )
```

### New Tests
```{r}
printDT(dife_t_br,
        rownames(dife_t_br)
        )
```


### Tests per 100K hab. 
```{r}
printDT(BrTests100kFormatted,
        rownames(BrTests100kFormatted)
        )
```


Mortality {data-navmenu="Brasil"}
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112"> Mortality Rate </b>
```{r, fig.height = 6, fig.width = 10}
BRstates <- c("SP", "RJ", "RS", "PE", "AM", "AP")

plotMortality(BrMortality, BRstates, "Brazil Mortality Rate by State")
```

### <b style = "color: #4c1112">  Daily variation of Mortality </b>
```{r, fig.height = 6, fig.width = 10}
dx <- 
BrMortality %>% 
  mutate_at(vars(-Dates), ~ . - lag(.)) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% 
  mutate_at(vars(-Dates), ~ round(., 2))

plotMortality(BrMortality, BRstates, "Brazil Mortality Rate Variation by State")
```




Cases {data-navmenu='Brasil - SP'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative after 100 cases </b>
```{r, fig.width = 10, fig.height = 6}


plot <- plotThis(SPCasesReg , rownames(SPCasesReg), ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")

# fig <- subplot(plotN$plotly, plotNE$plotly,plotCO$plotly,plotS_SE$plotly, nrows = 2, shareX = TRUE, shareY = FALSE, titleX = T, titleY = T)
# fig

plot$plotly

##ggsave(paste0(ggpath, "5BRCases.png"))

```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------
### Total Cases
```{r}
printDT(SPCasesFormatted,
        rownames(SPCasesFormatted)
        )
```

### Dif. Cases
```{r}
printDT(dife_c_sp,
        rownames(dife_c_sp)
        )
```


### Var. (%) 
```{r}
printDT(porce_c_sp/100,
        rownames(porce_c_sp)
        ) %>% DT::formatPercentage(1:5, 2)
```

Deaths {data-navmenu='Brasil - SP'} 
==========================================================================


Column {.tabset}
-----------------------------------------------------------------------
### <b style = "color: #4c1112" > Comparative after 10 Deaths </b>
```{r, fig.width = 10, fig.height = 6}


plot <- plotThis10(SPDeathsReg , rownames(SPDeathsReg), ytitle = "Confirmed Deaths", xtitle = "Days from 10 Deaths")

# fig <- subplot(plotN$plotly, plotNE$plotly,plotCO$plotly,plotS_SE$plotly, nrows = 2, shareX = TRUE, shareY = FALSE, titleX = T, titleY = T)
# fig

plot$plotly

##ggsave(paste0(ggpath, "5BRCases.png"))

```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------
### Total Deaths
```{r}
printDT(SPDeathsFormatted,
        rownames(SPDeathsFormatted)
        )
```

### Dif. Deaths
```{r}
printDT(dife_d_sp,
        rownames(dife_d_sp)
        )
```


### Var. (%) 
```{r}
printDT(porce_d_sp/100,
        rownames(porce_d_sp)
        ) %>% DT::formatPercentage(1:5, 2)
```


Doubling Time {data-navmenu='Brasil - SP'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}

doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}


Dates <- seq.Date(from = as.Date('2020-02-25'),
                  to   = HereBR,
                  by   = 'day')


da <- 
SPCasesReg %>% 
  t() %>% 
  as_tibble() %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(Dates)) %>% 
  filter(Days >= as.Date("2020-03-01"))


regs_sp <- rownames(SPCasesReg)

gg <- ggplot(da, aes(x = Days)) 
for (i in regs_sp) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = regs_sp)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
##ggsave(paste0(ggpath, "DoublingTime.png"))
```




SP Cases per day {data-navmenu='Brasil - SP'} 
==========================================================================

### Cases per day
```{r, fig.width = 10, fig.height = 12}
dz <- 
SPCasesReg %>% 
  
  
    rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna") %>%
  
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(SPCasesReg), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dd <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 


dh <- 
cbind(dz, dd) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:18], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- SPCasesReg[x,ncol(SPCasesReg)]
                           a <- list(
                                      text = paste0(x," - Total Cases:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```








SP Deaths per day {data-navmenu='Brasil - SP'} 
==========================================================================

### Deaths per day
```{r, fig.width = 10, fig.height = 12}
dz <- 
SPDeathsReg %>% 
  
  
    rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna") %>%
  
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(SPDeathsReg), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 16, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:18], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- SPDeathsReg[x,ncol(SPDeathsReg)]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```


SP - Data for Opening  {data-navmenu='Brasil - SP'}
==========================================================================

Row
--------------------------------------------------------------------

### Cases
```{r}
TABELA_R_eff <- dd %>%
mutate_all(~ .x/lag(.x,7)) %>%
mutate_if(~ any(is.infinite(.x)),~ replace(.x,is.infinite(.x),0)) %>%
mutate_if(~ any(is.na(.x)),~ replace(.x,is.na(.x),0)) %>%
mutate_all(~ round(.x,1))  %>%
rownames_to_column() %>%
pivot_longer(-rowname) %>%
pivot_wider(names_from=rowname, values_from=value) %>%
arrange_at(vars(last_col()))%>%
rename_all(~ c("RAs", format(seq.Date(from=as.Date("2020-02-25"),to=HereBR,by="days"),"%d/%m/%y"))) %>%
select("RAs",last_col(50:0))

m <-  TABELA_R_eff %>%
    column_to_rownames("RAs") %>%
    as.matrix()

colorScale <- data.frame(z=c(0,0.33,0.33,0.66,0.66,1),col=c("#008000","#008000","#FFFF00","#FFFF00", "#FF0000", "#FF0000"))
colorScale$col <- as.character(colorScale$col)



p <- plot_ly(x=colnames(m), y=rownames(m), z = m, zmin=0,zmax=3, zsmooth=FALSE, ygap =0.25,xgap =0.25, colorscale=colorScale, type = "heatmap") 
p


```





### Deaths
```{r}


TABELA_R_eff <- dw %>%
mutate_all(~ .x/lag(.x,7)) %>%
mutate_if(~ any(is.infinite(.x)),~ replace(.x,is.infinite(.x),0)) %>%
mutate_if(~ any(is.na(.x)),~ replace(.x,is.na(.x),0)) %>%
mutate_all(~ round(.x,1))  %>%
rownames_to_column() %>%
pivot_longer(-rowname) %>%
pivot_wider(names_from=rowname, values_from=value) %>% 
arrange_at(vars(last_col()))%>%
rename_all(~ c("RAs", format(seq.Date(from=as.Date("2020-02-25"),to=HereBR,by="days"),"%d/%m/%y"))) %>%
select("RAs",last_col(50:0))

m <-  TABELA_R_eff %>%
    column_to_rownames("RAs") %>%
    as.matrix()

colorScale <- data.frame(z=c(0,0.17,0.17,0.33,0.33,0.66,0.66,1),col=c("#008000","#008000","#FFFF00","#FFFF00","#ffa500", "#ffa500", "#FF0000", "#FF0000"))
colorScale$col <- as.character(colorScale$col)



p <- plot_ly(x=colnames(m), y=rownames(m), z = m, zmin=0 , zmax=3, zsmooth=FALSE, ygap =0.25,xgap =0.25, colorscale=colorScale, type = "heatmap") 
p


```







Comparative After 100 cases  {data-navmenu='Figures'}
====================================================================

Column {.tabset}
--------------------------------------------------------------------

### <b style = "color: #4c1112">  Cases relation with exponential growth </b>
```{r, fig.height = 6, fig.width = 10}
countries <- c("Italy", "Spain", "Brazil", "United States", "United Kingdom", "Germany","France")

plot <- plotThis(WorldCases, countries, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
p    <- plot$plotly

N <- 
WorldCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(countries) %>% 
  summarise_all(~ sum(if_else(. > 100, 1, 0))) %>% 
  max

daysToDouble <- c(3,4,7)
Nd <- length(daysToDouble)
n  <- round(N/1.25)
exdf <- NULL
for (i in daysToDouble) {
     range     <- seq(ceiling(i*log(100, 2)), length.out = n)
     expVector <- vapply(range, function(d) 2**(d/i), numeric(1))
     exdf      <- cbind(exdf, expVector)
}
d0f <- as_tibble(exdf) %>% rename_all(~ paste0("V", 1:Nd)) %>% add_column(Days = 0:(n-1))

for (days in 1:Nd) {
  p <- p %>% add_lines(data = d0f, x = ~Days, y = as.formula(paste0('~V', days)), name = paste0('V', days), 
                       line = list(color = 'rgb(205, 12, 24)', dash = 'dot', width = 1),
                       showlegend = FALSE)
}

d10f <- log10(d0f)

A1 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(5),
  y = d10f[n,1] + 0.2,
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 3 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

A2 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(5),
  y = d10f[n,2] + 0.2,
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 4 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

A3 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(5),
  y = d10f[n,3] + 0.2,
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 7 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

p <- p %>% layout(annotations = A1)
p <- p %>% layout(annotations = A2)
p <- p %>% layout(annotations = A3)

p

ggfig <- 
plot$ggplot + 
  geom_line(d0f, mapping = aes(y = V1), linetype = 'dashed', color = "#CD0C0E") + 
  annotate('text', x = 55, y = d0f[n,1,drop=T] + 1.0e7, label = "Doubles every 3 days", color = "#CD0C0E") +
  geom_line(d0f, mapping = aes(y = V2), linetype = 'dashed', color = "#CD0C0E") +
  annotate('text', x = 55, y = d0f[n,2,drop=T] + 0.5e6, label = "Doubles every 4 days", color = "#CD0C0E") +
  geom_line(d0f, mapping = aes(y = V3), linetype = 'dashed', color = "#CD0C0E") +
  annotate('text', x = 55, y = d0f[n,3,drop=T] + 0.1e5, label = "Doubles every 7 days", color = "#CD0C0E") 
##ggsave(paste0(ggpath,"7CasesExp.png"))
```

### <b style = "color: #4c1112">  Deaths relation with exponential growth </b>
```{r, fig.height = 6, fig.width = 10}

countries <- c("Italy", "Spain", "Brazil","United States", "United Kingdom", "Germany","France")

plot <- plotThis(WorldDeaths, countries, ytitle = "Confirmed Deaths", xtitle = "Days from 100 Deaths")
p    <- plot$plotly

N <- 
WorldDeaths %>% 
  t() %>% 
  as_tibble() %>% 
  select(countries) %>% 
  summarise_all(~ sum(if_else(. > 100, 1, 0))) %>% 
  max

daysToDouble <- c(3,4,7)
Nd <- length(daysToDouble)
n  <- round(N/1.45)
exdf <- NULL
for (i in daysToDouble) {
     range     <- seq(ceiling(i*log(100, 2)), length.out = n)
     expVector <- vapply(range, function(d) 2**(d/i), numeric(1))
     exdf      <- cbind(exdf, expVector)
}
d0f <- as_tibble(exdf) %>% rename_all(~ paste0("V", 1:Nd)) %>% add_column(Days = 0:(n-1))

for (days in 1:Nd) {
  p <- p %>% add_lines(data = d0f, x = ~Days, y = as.formula(paste0('~V', days)), name = paste0('V', days), 
                       line = list(color = 'rgb(205, 12, 24)', dash = 'dot', width = 1),
                       showlegend = FALSE)
}

d10f <- log10(d0f)

A1 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(4 - 0.1),
  y = d10f[n,1],
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 3 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

A2 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(4),
  y = d10f[n,2] + 0.2,
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 4 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

A3 <- list(
  xref = 'paper',
  yref = 'y',
  x = log10(4),
  y = d10f[n,3],
  type = "log",
  xanchor = 'left',
  yanchor = 'middle',
  text = ~"Doubles every 7 days",
  font = list(family = 'Arial',
              size = 9.9,
              color = 'rgba(205,12,24,1)'),
  showarrow = FALSE)

p <- p %>% layout(annotations = A1)
p <- p %>% layout(annotations = A2)
p <- p %>% layout(annotations = A3)

p

ggfig <- 
plot$ggplot + 
  geom_line(d0f, mapping = aes(y = V1), linetype = 'dashed', color = "#CD0C0E") + 
  annotate('text', x = 55, y = d0f[n,1,drop=T] + 1.0e7, label = "Doubles every 3 days", color = "#CD0C0E") +
  geom_line(d0f, mapping = aes(y = V2), linetype = 'dashed', color = "#CD0C0E") +
  annotate('text', x = 55, y = d0f[n,2,drop=T] + 0.5e6, label = "Doubles every 4 days", color = "#CD0C0E") +
  geom_line(d0f, mapping = aes(y = V3), linetype = 'dashed', color = "#CD0C0E") +
  annotate('text', x = 55, y = d0f[n,3,drop=T] + 0.1e5, label = "Doubles every 7 days", color = "#CD0C0E") 
##ggsave(paste0(ggpath,"8DeathsExp.png"))
```

Doubling Time {data-navmenu='Figures'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}
countries <- c("United States"
             
              ,"Italy"
              ,"Germany"
              ,"United Kingdom"
             
              ,"Brazil"
              ,"Sweden"
              ,"Japan"
              )

doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}

da <- 
WorldCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(all_of(countries)) %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(DatesWorld)) %>% 
  filter(Days >= as.Date("2020-03-02"))

gg <- ggplot(da, aes(x = Days)) 
for (i in countries) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = countries)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
##ggsave(paste0(ggpath, "DoublingTime.png"))
```

Total Cases After Lockdown {data-navmenu='Figures'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Cases after lockdown </b>
```{r, fig.height = 6, fig.width = 10}
countries       <- c('Germany', 'France', 'Spain', 'Italy', 'United Kingdom', 'Austria', 'Denmark', 'Norway')
lockdown        <- c("2020-03-22", "2020-03-17", "2020-03-14", "2020-03-08", "2020-03-23", "2020-03-15", "2020-03-13", "2020-03-12")
names(lockdown) <- countries

lockdownPlot(dife_c, countries, lockdown, DatesWorld)
```

### <b style = "color: #4c1112">  Deaths after lockdown </b>
```{r, fig.height = 6, fig.width = 10}
lockdownPlot(dife_d, countries, lockdown, DatesWorld)
```

### <b style = "color: #4c1112">  Cases variation after lockdown </b>
```{r, fig.height = 6, fig.width = 10}
lockdownPlot(porce_c, countries, lockdown, DatesWorld)
```

### <b style = "color: #4c1112">  Deaths variation after lockdown </b>
```{r, fig.height = 6, fig.width = 10}
lockdownPlot(porce_d, countries, lockdown, DatesWorld)
```
