---
title: "Covid-19: Brasil"
output: 
  flexdashboard::flex_dashboard:
    css: style.css
    orientation: rows
    vertical_layout: scroll
  rmarkdown:: github_document
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(sidrar)
library(xlsx)
library(dplyr)
library(leaflet)







# Some color schemes: 

# hex msafra: #4c1211
# rgb msafra: 761817
plotlyColors <-   c('#740001',
                    '#005b96',
                    '#23272a',
                    '#d3a625',
                    '#008744',
                    '#fb2e01',
                    '#01cdfe',
                    '#99aab5',
                    '#ffc425',
                    '#00b159',
                    '#d11141',
                    '#00aedb',
                    '#777777',
                    '#ffe28a',
                    '#6fcb9f',
                    '#0057e7',
                    '#ae0001',
                    '#05ffa1',
                    '#b967ff',
                    '#7289da',
                    '#f37735',
                    '#666547',
                    '#d62d20',
                    '#6497b1',
                    '#b3cde0',
                    '#ff4d00',
                    '#66545e',
                    '#a39193',
                    '#aa6f73',
                    '#eea990'
                    )




 
# Setting time span: Watch out the time of updating
dias <- ceiling(difftime(Sys.Date(), "2020-01-22", units = "days")) #-1

# Choose here the path to output png plots:
ggpath  <- "C:/Users/Padulla/Documents/GitHub/corona_dash/"
Here    <- Sys.Date()

HereBR  <- Here - 0

# loading stuff
source("Functions.R")
source("Brazil.R")


```

Main {data-navmenu='Cases'} 
==========================================================================

Column 
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Cases Map </b>
```{r, fig.width = 10, fig.height = 6}

BrEstados <- geojsonio::geojson_read("C:/Users/Padulla/Documents/GitHub/corona_dash/GEOjson/brazil-states.geojson", what = "sp")

BrEstados@data <- BrEstados@data %>% tibble:: add_column(BrCasesDia) 


bins <- c(100, 200, 400, 800, 1000, 1500, 2500, 4000,5000,10000,15000,20000,25000,30000,40000, Inf)
pal <- colorBin("Blues", domain = BrEstados@data$BrCasesDia$totalCases, bins = bins)




m <- leaflet(BrEstados) %>%
  setView(-50, -16, 3.5) %>% addTiles()



labels <- sprintf(
  "<strong>%s</strong><br/>%g people",
  BrEstados@data$name, BrEstados@data$BrCasesDia$totalCases
) %>% lapply(htmltools::HTML)






m <- m %>% addPolygons(
  fillColor = ~pal(BrEstados@data$BrCasesDia$totalCases),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "5",
  fillOpacity = 2,
  highlight = highlightOptions(  weight = 5,    color = "#666",    dashArray = "",    fillOpacity = 0.7,    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = "Total Cases",
    position = "bottomright" )

m



```


### <b style = "color: #4c1112" > Comparative after 100 cases </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

S_SE <- c("SP"
           ,"RJ"
           ,"MG"
           ,"RS"
           ,"PR"
           ,"SC"
           ,"ES"
           )


Norte <- c("AM"
           ,"PA"
           ,"AC"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"RR"
           )


CO <- c("DF"
        ,"GO"
           ,"MS"
           ,"MT"
           )

NE <- c("CE"
         ,"BA"
           ,"PE"
           ,"MA"
           ,"SE"
           ,"AL"
           ,"PB"
           ,"PI"
           ,"RR"
           )


plotN <- plotThis(BrCases, Norte, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotNE <- plotThis(BrCases, NE, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotS_SE <- plotThis(BrCases, S_SE, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")
plotCO <- plotThis(BrCases, CO, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")


plot <- plotThis(BrCases, states, ytitle = "Confirmed Cases", xtitle = "Days from 100 Cases")

# fig <- subplot(plotN$plotly, plotNE$plotly,plotCO$plotly,plotS_SE$plotly, nrows = 2, shareX = TRUE, shareY = FALSE, titleX = T, titleY = T)
# fig

plot$plotly

ggsave(paste0(ggpath, "5BRCases.png"))

```

### <b style = "color: #4c1112" > Comparative after 10 cases per 100.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis10(BrCasesPop, states, ytitle = "Confirmed Cases", xtitle = "Days from 10 Cases")
plot$plotly
ggsave(paste0(ggpath, "BRCasespop.png"))

```



Column {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Cases
```{r}
printDT(BrCasesFormatted,
        rownames(BrCasesFormatted)
        )
```

### New Cases
```{r}
printDT(dife_c_br,
        rownames(dife_c_br)
        )
```


### Var. (%)
```{r}
printDT(porce_c_br / 100,
        rownames(porce_c_br)
       ) %>% DT::formatPercentage(1:5, 2)
```


Cases per day Graphs {data-navmenu='Cases'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Cases per day
```{r, fig.width = 10, fig.height = 12}
dz <- 
BrCases %>% 
  
  rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna") %>%
  
  
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrCases), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))




dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 14, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:29], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- BrCases[x,ncol(BrCases)]
                           a <- list(
                                      text = paste0(x," - Total Cases:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```

SP {data-navmenu='Cases'} 
==========================================================================

Column
-----------------------------------------------------------------------
```{r, fig.width = 10, fig.height = 12}











# m <- BrCasesPop+1  %>% log
# m <- as.matrix(m)
# 
# 
# p <- plot_ly(x=colnames(m), y=rownames(m), z = m, type = "heatmap") %>%
#     layout(margin = list(l=120))
# p
# 
# 
# 
# heatmap(m, Colv = NA, Rowv = NA, xlab="Date",ylab="States", main="Cases per capita")

```

Doubling Time {data-navmenu='Cases'}
====================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112">  Time to double cases </b>
```{r, fig.height = 6, fig.width = 10}
countries <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

doublingTime <- function(x) {
  y <- x - dplyr::lag(x) 
  x / y
}


Dates <- seq.Date(from = as.Date('2020-02-25'),
                  to   = HereBR,
                  by   = 'day')


da <- 
BrCases %>% 
  t() %>% 
  as_tibble() %>% 
  select(all_of(countries)) %>% 
  mutate_all(~ TTR::SMA(., 7)) %>% 
  mutate_all(doublingTime) %>% 
  mutate(Days = as.Date(Dates)) %>% 
  filter(Days >= as.Date("2020-03-02"))

gg <- ggplot(da, aes(x = Days)) 
for (i in countries) {
  gg <- gg + geom_line(aes_(y = as.name(i),  colour = i), na.rm = TRUE) +
             geom_point(aes_(y = as.name(i), colour = i), na.rm = TRUE)
}
gg <- gg + labs(x = "Days", y = "Doubling Time")
gg <- gg + theme(legend.position = 'bottom') +
           scale_color_manual("", values = plotlyColors, breaks = countries)

ggplotly(gg, height = 500, width = 1200) %>%
  layout(legend = list(orientation = 'h', x = +0.05, y = -0.15))
ggsave(paste0(ggpath, "DoublingTime.png"))
```




Main {data-navmenu='Deaths'} 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Comparative after 100 deaths </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis(BrDeaths, states, ytitle = "Confirmed Deaths", xtitle = "Days from 100 Deaths")
plot$plotly
ggsave(paste0(ggpath, "6BRDeaths.png"))





```


<!-- Column  -->
<!-- ----------------------------------------------------------------------- -->
### <b style = "color: #4c1112" > Comparative after 10 deaths per 1.000.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
states <- c("SP"
           ,"RJ"
           ,"CE"
           ,"MG"
           ,"RS"
           ,"DF"
           ,"PR"
           ,"BA"
           ,"AM"
           ,"SC"
           ,"RN"
           ,"PE"
           ,"ES"
           ,"MA"
           ,"GO"
           ,"PA"
           ,"MS"
           ,"MT"
           ,"AC"
           ,"SE"
           ,"AL"
           ,"TO"
           ,"RO"
           ,"AP"
           ,"PB"
           ,"PI"
           ,"RR"
           )

plot <- plotThis10(BrDeathsPop, states, ytitle = "Confirmed Deaths", xtitle = "Days from 10 Deaths")
plot$plotly
ggsave(paste0(ggpath, "BRDeathspop.png"))
```


### <b style = "color: #4c1112" > Comparative Official and States </b>
```{r, fig.width = 10, fig.height = 6}

dmb1 <- BrDeaths    %>%   t %>%   as_tibble  %>% select ('Brasil') %>% rename(BrasilS=Brasil)
dmb2 <- BrDeathsMS        %>% t  %>% as_tibble        %>% select ('Brasil') %>% rename(BrasilMS=Brasil)
dmb3 <- BrDeaths_dif        %>% t  %>% as_tibble        %>% select ('Brasil') %>% rename(BrasilD=Brasil)


dmb <- cbind(dmb1,dmb2)

dmb <- dmb %>% 
  as_tibble %>%        
  #mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>%   select(Dates, everything())  %>% 
  filter(Dates >= as.Date("2020-03-29"))

dmb3 <- dmb3 %>% 
  as_tibble %>%        
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>%   select(Dates, everything())  %>% 
  filter(Dates >= as.Date("2020-03-29"))




fig1 <- plot_ly(
  x = dmb$Dates,
  y = dmb$BrasilS,
   name = 'States',
  type = "bar",
  color = I("firebrick4")
) %>%
layout(
     title = "Official vs States",
     xaxis = list(title = "Date",
     categoryorder = "array",
     categoryarray = ~dmb$Dates),
     yaxis = list(title = "Deaths")
)

fig1 <- fig1 %>% add_trace(y = dmb$BrasilMS, name = 'Official',
  color = I("dimgrey"))






fig2 <- plot_ly(
  x = dmb3$Dates,
  y = dmb3$BrasilD,
   name = 'States',
  type = "bar",
  color = I("dodgerblue4")
) %>%
layout(
     title = "Difference (States-Official)",
     xaxis = list(title = "Date",
     categoryorder = "array",
     categoryarray = ~dmb3$Dates),
     yaxis = list(title = "Deaths")
)







p <- subplot(fig1, fig2,  nrows = 2, shareX = FALSE, shareY = FALSE)
p





```


Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Deaths
```{r}
printDT(BrDeathsFormatted,
        rownames(BrDeathsFormatted)
       )
```


### New Deaths
```{r}
printDT(dife_d_br,
        rownames(dife_d_br)
      )
```


### Var. (%)
```{r}
printDT(porce_d_br / 100,
        rownames(porce_d_br)
       ) %>% DT::formatPercentage(1:5, 2)
```


Deaths per day Graphs {data-navmenu='Deaths'} 
==========================================================================

Column
-----------------------------------------------------------------------

### Deaths per day
```{r, fig.width = 10, fig.height = 12}
dz <- 
BrDeaths %>% 
  
  
    rownames_to_column(var = "NovaColuna") %>%
       arrange_at(vars(last_col()), desc) %>%
       select(NovaColuna, everything())  %>%
      column_to_rownames("NovaColuna") %>%
  
  t %>% 
  as_tibble %>% 
  mutate_all(~ . - lag(.)) %>% 
  mutate(Dates = as.Date(colnames(BrDeaths), format = "%m/%d/%y") ) %>% 
  select(Dates, everything()) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .))

dw <- 
do.call(cbind, lapply(colnames(dz)[-1], function(x) TTR::SMA(dz[,x], 7))) %>% 
  as_tibble %>% 
  rename_all(~ paste0('M',colnames(dz)[-1])) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 

dh <- 
cbind(dz, dw) %>% 
  as_tibble %>% 
  filter(Dates >= as.Date("2020-03-20"))

f2 <- list(family = 'Old Standard TT, serif', size = 14, color = ("#4c1112"))

plots <- 
lapply(colnames(dh)[2:29], function(x){ 
                           expr   <- paste0("~", "`", x, "`")
                           mexpr  <- paste0("~", "`", "M", x, "`")
                           legm   <- paste0("Moving average of ", x)
                           t <- dh[nrow(dh),x]
                           tt <- BrDeaths[x,ncol(BrDeaths)]
                           a <- list(
                                      text = paste0(x," - Total Deaths:",tt," - Last data:",t),
                                      font = f2,
                                      xref = "paper",
                                      yref = "paper",
                                      yanchor = "bottom",
                                      xanchor = "center",
                                      align = "center",
                                      x = 0.5,
                                      y = 1,
                                      showarrow = FALSE
                                    )
                           plot_ly(dh, x = ~Dates) %>% 
                             add_trace(y = as.formula(expr),  type = 'bar', color = I("firebrick4")) %>% 
                             add_trace(y = as.formula(mexpr), type = 'scatter', mode = 'lines', color = I("black") ) %>% 
                             layout(showlegend = FALSE, annotations = a)
})
names(plots) <- colnames(dz)[-c(1, length(dz))]
p <- subplot(plots, nrows = 7, shareX = FALSE, shareY = FALSE)
p
```





Tests
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112" > Tests </b>
```{r, fig.width = 10, fig.height = 6}
tg <- BrTests %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("States", "Tests")) %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 
tg <-tg[-c(28,29), ] 
tg <- arrange(tg,desc(Tests))


  
fig <- plot_ly(
  x = tg$States,
  y = tg$Tests,
  type = "bar",
  color = I("Gray")
) %>%
layout(
     title = "Total Tests",
     xaxis = list(title = "States",
     categoryorder = "array",
     categoryarray = ~tg$States),
     yaxis = list(title = "Tests")
)

fig

```

### <b style = "color: #4c1112" > Tests 100.000 hab </b>
```{r, fig.width = 10, fig.height = 6}
tg <- BrTestsP100k %>% 
        tibble::rownames_to_column() %>% 
        select(1, last_col()) %>% 
        rename_all(~ c("States", "Tests")) %>% 
        mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) 
tg <-tg[-c(28,29), ] 
tg <- arrange(tg,desc(Tests))


  
fig <- plot_ly(
  x = tg$States,
  y = tg$Tests,
  type = "bar",
  color = I("firebrick4")
) %>%
layout(
     title = "Total Tests per 100k hab.",
     xaxis = list(title = "States",
     categoryorder = "array",
     categoryarray = ~tg$States),
     yaxis = list(title = "Tests per 100k hab.")
)

fig

```

Row {data-width=350, data-height=350}
-----------------------------------------------------------------------

### Total Tests
```{r}
printDT(BrTestsFormatted,
        rownames(BrTestsFormatted)
        )
```

### New Tests
```{r}
printDT(dife_t_br,
        rownames(dife_t_br)
        )
```


### Tests per 100K hab. 
```{r}
printDT(BrTests100kFormatted,
        rownames(BrTests100kFormatted)
        )
```


Mortality 
==========================================================================

Column {.tabset}
-----------------------------------------------------------------------

### <b style = "color: #4c1112"> Mortality Rate </b>
```{r, fig.height = 6, fig.width = 10}
BRstates <- c("SP", "RJ", "RS", "PE", "AM", "AP")

plotMortality(BrMortality, BRstates, "Brazil Mortality Rate by State")
```

### <b style = "color: #4c1112">  Daily variation of Mortality </b>
```{r, fig.height = 6, fig.width = 10}
dx <- 
BrMortality %>% 
  mutate_at(vars(-Dates), ~ . - lag(.)) %>% 
  mutate_if(~ any(is.na(.)), ~ if_else(is.na(.), 0, .)) %>% 
  mutate_at(vars(-Dates), ~ round(., 2))

plotMortality(BrMortality, BRstates, "Brazil Mortality Rate Variation by State")
```

